%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Casey Stella
\documentclass[margin,line,12pt]{resume}
\usepackage{fancyhdr}
\usepackage{hyperref}
\pagestyle{fancy}

\fancyhead{}
\fancyfoot{}

\setlength{\headheight}{15pt}

\fancyhead[CO, CE]{Casey Stella}
\fancyfoot[RO, LE]{\thepage}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Casey Stella}
\begin{resume}
    \thispagestyle{empty}
    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    Address Available             \hfill {\bf github:} \url{http://github.com/cestella} \vspace{0mm}\\\vspace{0mm}%
    Upon Request                  \hfill {\bf e-mail:} cestella@gmail.com       \vspace{0mm}\\\vspace{-4.5mm}%

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}
    \textbf{Hortonworks}, San Jose, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Principal Architect} \hfill \textbf{November 2012 -- Present}\\
    As a Principal Architect in the consulting services organization at Hortonworks, I provide
    mentorship and guidance in operationalizing Hadoop and its ecosystem to solve business problems
    for our clients.  I work with our clients to reduce risk and time to market by providing expertise 
    in big data.

    \begin{list2}
    \item  Provide proof-of-concepts to reduce engineering churn
    \item  Give extensive presentations about the Hadoop ecosystem, best practices, data architecture in Hadoop
    \item  Provide mentorship and guidance to other architects to help them become independent
    \item  Provide review and feedback for existing physical architecture, data architecture and individual code
    \item  Debug and solve issues with Hadoop as on-the-ground subject matter expert.  This could include everything from patching components to post-mortem analysis of errors.
    \end{list2}

    I focus on issues around data science and especially natural language processing at scale. I have domain knowledge in medical/clinical informatics and oil/gas data analysis and signal processing.

    \textbf{Explorys}, Cleveland, OH \vspace{2mm}\\\vspace{1mm}%
    \textsl{``Big Data'' Architect} \hfill \textbf{January 2011 -- November 2012}\\
    I was a ``big data'' architect and, prior to that, a senior software engineer on the platform team at Explorys. 
    The team was responsible for the creation, care and maintenance of the high performance indexing infrastructure.
    My job required a deep understanding of the Hadoop ecosystem.  I designed the next generation data 
    architecture for the unstructured data at Explorys as well as writing, debugging, and analyzing the 
    performance of many map reduce jobs to realize that architecture.  

    \begin{list2}
    \item  Devised and lead the implementation of the next generation architecture for more efficient data ingestion and processing.
    \item  Proficiency with mentoring and on-boarding new engineers who are not proficient in Hadoop and getting them up to speed quickly.
    \item  Experience with being a technical lead of a team of engineers.
    \item  Proficiency with modern natural language processing and general machine learning techniques and approaches
    \item  Extensive experience with Hadoop and HBase, including multiple public presentations about these technologies.
    \item  Experience with hands on data analysis and performing under pressure.
    \item  Designed and wrote a layer on top of MapReduce to make the task of writing MapReduce jobs easier and more safe for Junior Engineers.
    \item  Contributed much of the code in our open source project: \\\url{http://github.com/ExplorysMedical/Apothecary}
    \end{list2}

    \newpage
    \vspace*{1mm}

    \textbf{Game Communications}, Mayfield Heights, OH \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Engineer} \hfill \textbf{November 2009 -- January 2011}\\
    Designed, implemented and integrated into legacy code a scalable network infrastructure layer for an instant message and VOIP network
    \begin{list2}
    \item Created a software routing layer and implementing an ordered, reliable protocol on top of the raw network layer
    \item Integrated Cassandra as a distributed persistent metadata store to provide metadata resolution for network entities on the network
    \item Created low-level network libraries in C++ and C\# to send messages across network
    \item Spearheaded institution of pair-programming and semi-agile practices
    \end{list2}
    \textbf{ION Geophysical}, Houston, TX \vspace{2mm}\\\vspace{1mm}%
    \textsl{Research Geophysicist} \hfill \textbf{October 2008 -- November 2009}\\
    Member of the time processing R\&D team, tasked to design, prototype and implement production-ready algorithms to use applied math and signal processing to reduce noise in seismic data.  This was a telecommuting position from Cleveland, OH.
    \begin{list2}
    \item Implemented multithreaded C++ applied linear algebra library consisting of efficient STL-compliant data structures and algorithms to assist in signal processing
    \item Assisted in the design and implementation of an internal flow-based map-reduce system for doing distributed scientific computation
    \item Used Tokyo Cabinet to provide an on-disk index of seismic metadata in an efficient way
    \item Implemented a multidimensional least squares adaptive filter that decreased wall-clock time for our most common seismic task by an order of magnitude
    \item Developed a fixed-precision algorithm in C for the embedded PowerPC 405 platform which uses first-order statistics to differentiate noise from initial signal in an accurate, efficient and robust way
    \item Spearheaded institution of pair-programming and semi-agile practices in a geographically dispersed environment
    \end{list2}

%    \newpage
%    \vspace*{1mm}
    
    \textbf{Oracle}, Cleveland, OH \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Member of Technical Staff} \hfill \textbf{October 2005 -- October 2008}\\
    Member of the Oracle Enterprise Repository team.  We provided an enterprise J2EE application to organize and manage assets and their metadata. 
    \begin{list2}
    \item Worked as part of a geographically distributed team using agile practices
    \item Designed and implemented an enterprise build system around Maven, porting an existing heterogeneous build system from Ant and shell scripts to Maven
    \item Implemented multiple performance and scalability improvements, resulting in substantial benefits deriving from better caching strategies and algorithms with more favorable CPU/Memory complexity characteristics.
    \item Managed summer interns
    \end{list2}
    
    \newpage
    \vspace*{1mm}

    %__________________________________________________________________________________________________________________
    % Certifications
    \section{\mysidestyle Certification}
    \textbf{Cloudera Certified Hadoop Developer} \hfill \textbf{August 2012}\\
    \textbf{Cloudera Certified HBase Developer} \hfill \textbf{August 2012}

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{Texas A\&M University}, College Station, TX \vspace{2mm}\\\vspace{1mm}%
    \textsl{Masters of Science in Mathematics} \hfill \textbf{ Spring 2005}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Emphasis in Computational Complexity and Theoretical Computer Science
        \item Advised by Dr. J. Maurice Rojas
    \end{list2}\vspace{-1.5mm}
    
    \textbf{University of Louisiana at Monroe}, Monroe, LA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bachelors of Science in Mathematics and Computer Science} \hfill \textbf{ Spring 2002}\vspace{-3mm}\\\vspace{-1mm}%

%__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Selected Publications, Patents \& Talks}
    
    ``Fast Map Reduce over HBase'',\\
    \textsl{Strata/Hadoop World Apache HBase Meetup, NYC}, Invited Talk

    ``New Complexity Thresholds for Sparse Real Polynomials'',\\
    \textsl{Sixth International Joint Meeting of AMS and SMM}, Invited Talk

    ``SYSTEM AND METHOD FOR USING AN EDITABLE LIFECYCLE EVENT DISTRIBUTION LIST WITH A SERVICE METADATA REPOSITORY'',\\
    \textsl{Patent Issued March 27, 2012}, Patent number 8145680, Oracle Corporation

    J. Maurice Rojas, Frederic Bihan, and Casey Stella\\
    ``Faster Real Feasibility via Circuit Discriminants'',\\
    In \textsl{Proceedings of ISSAC 2009}, pp. 39-46, ACM Press, 2009.

    
    
    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honors and\\Awards} 

    Outstanding Teaching Assistant [2005]                                                           \vspace{1mm}\\
    National Science Foundation VIGRE Fellowship [2004]                                             \vspace{1mm}\\
    AUF \& Regents Fellowships for Oustanding Academic Achievement [2003]                           

    %__________________________________________________________________________________________________________________
    % Computer Skills
    %\section{\mysidestyle Programming} 
    %C, C++, Matlab, Linux shell scripting, Perl, Python, \LaTeXe, PBS, SQL, Java, .NET, SPSS.



    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}




%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

